Title

### 2018-09-01 thesis/paper/paper.tex
Improved symmetric

\subsection{Symmetric (Q21510862)}
The symmetric constraint requires an additional statement on the value of a constrained statement with the constrained property and the constrained item as value. It is thus equal to an inverse constraint (see \ref{subsec_2_inverse}) with the same property as constrained property and required property and will not be elaborated on.

The symmetric constraint can be translated exactly as the inverse constraint if the inverse property where set to the same as the constrained property.

>>>>

\subsection{Symmetric (Q21510862)}
The \emph{symmetric} constraint requires an additional statement on the value of a constrained statement with the constrained property and the constrained item as value. It is thus equal to an \emph{inverse} constraint (see \ref{subsec_2_inverse}) with the same property as constrained property and inverse property. It can be translated exactly as the inverse constraint if the inverse property where set to the same as the constrained property.
